Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-03 Cover_letter_JPM.tex
Updates from Overleaf

@@

\section*{Response to Reviewer 1 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

@@

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested  candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.

%%{
(ok)Result altered to CAMK2N1, IL19; 
Supplementary;
Discussion:
([ok] 3.2, 3.3 remained validated by GSE2837)
(ok) new Figure4.pdf  KM plots
(ok)table 1 (6 genes), (ok) table 2 (4 genes)

Table 3: CAMK2N1 (ok)
Table 4: IL19  (ok)

six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%%}

2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
\end{MyColorPar}

@@

\subsection*{1-2}
%
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

@@

One day in February 2021, after meditation in the morning, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to say "Stress is also be a kind of biomarker of HNSCC in the future study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it was shown here in the following paragraph.
\begin{MyColorPar}{red}
"
"
\end{MyColorPar} %red
\end{MyColorPar} % blue
%Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
%epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
%The usefulness of multi-omics data for the prediction of HNSCC outcome %is expected.
%such as the (censored) survival time.

@@

% strategy should changing; run GCP Rstudio? hard work to do
In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.

@@

\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data. It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:

@@

In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
\end{MyColorPar}

@@

\subsection*{2-6}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

@@

% (ok)
We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new Figure 1 with clear direction of the workflow.
A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
In Figure 2, the ticks and labels on the x-axis were corrected.

%%
\begin{MyColorPar}{black} % minor comment
***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
\end{MyColorPar}

Answer
We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.

\begin{MyColorPar}{red}
% EdgeR
Some researchers\cite{Xu2021a} tried to find DEGs of gene expression data (without survival information) for HNSCC biomarker discovery.
RNA-Seq data were downloaded from The Cancer Genome Atlas (TCGA) database or other GSE datasets (e.x. GSE30784: 167 OSCC samples and 45 normal controls) from the Gene Expression Omnibus. 
We employed DAVID (https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function. The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was used to annotate the potential functions.
%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
and the protein-protein interaction (PPI) network was conducted to identify differentially expressed genes (DEGs) closely associated with HNSCC.
the pathway enrichment analysis of DEGs was performed by DAVID, String, and Sytoscape software programs\cite{Huang2019}\cite{Shen2019}.
The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score >0.9, and the PPI network was visualized in Cytoscape (Version 3.7.1) software. Moreover, genes with degree> = 25 were selected as hub genes. Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.

.. by integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses. The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software. GOfunctional annotation and KEGG pathway analyses were performed using the Database for Annotation, Visualization, and Integrated Discovery. Hub genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA) and the Human Protein Atlas (HPA) website.

@@

% Cox Risk Regression Establishment and Validation with lncRNA data
OSCC samples were randomly divided into a training set and a validation set. Univariate Cox regression was used to select prognosis-associated genes (p < 0.05). Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
establish a prognostic risk score model, and the penalty regularization parameter lambda (λ) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
%https://glmnet.stanford.edu/articles/glmnet.html
Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation
Finally, a validation set and Kaplan–Meier survival curves along with a logrank p test were applied to validate its accuracy. In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
Biomarkers Screening and Validation
The status and survival time of OSCC patients were extracted. Subsequently, the mRNA was enrolled in the PPI and ceRNA networks, and lncRNA and miRNA identified in ceRNA were selected for screening biomarkers. We used univariate Cox regression to screen prognostic factors (p < 0.05), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (p < 0.01) were selected as primitive biomarkers. 
Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these biomarkers. In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.

%\subsubsection{from TCGA to expression biomarkers} 
%%% how other researchers used TCGA to find expression biomarkers
Usually, researchers used TCGA to find expression biomarkers...
% reference https://www.biostars.org/p/153013/
Tutorial: Survival analysis of TCGA patients
#integrating gene expression (RNASeq) data Why would you want to do survival
#analysis based on gene expression data? Well, let's say you have a number of
#genes that you are interested in and they are differentially expressed between
#tumor and normal samples, it would be very powerful to show that alteration in
#gene expression correlates with worse survival or earlier tumor recurrence.
% https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
% from Mary Goldman and Jing Zhu, UCSC Cancer Browser
% https://genome-cancer.ucsc.edu/

@@

%%%***[latex line 410]
\begin{MyColorPar}{black} % minor comment
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
\end{MyColorPar}

@@

\begin{MyColorPar}{red}
%%%
There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
First, although \acrshort{tcga} genomics data has been harmonized, 
%two things were found during our investigating and data cleaning:
the preprocessing of TCGA RNA-Seq is as follows:

\begin{outline}
\1 HNSCC samples without complete clinical information have been removed;
\1 null expressed genes in more than half of the HNSCC samples have been excluded;
\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be updated from 20499 to 20500;
%
that is because of ...
%[main\_marginSFP\_HNSCC.R] line 1361
osccT_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
event (alive) to censored (status 0) % to handle missing data of censored by OS_months imputation
R help from Jorge I Velez
[line 1654]
for gene correction (20499 to 20500) from SLC35E2A to 2 genes:
% SLC35E2A: 9906
% SLC35E2B: 728661
\end{outline}

>>>>

\usepackage[bf]{caption}
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}

@@

\section*{Response to Reviewer 1 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point answer to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

@@

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested  candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
2) Since that revision, we added holistic cancer care in the discussion section (please see Answer 1-2).% \ref{page:1-2}).

%%{
%(ok)Result altered to CAMK2N1, IL19; 
%Supplementary;
%Discussion:
%([ok] 3.2, 3.3 remained validated by GSE2837)
%(ok) new Figure4.pdf  KM plots
%(ok)table 1 (6 genes), (ok) table 2 (4 genes)

%Table 3: CAMK2N1 (ok)
%Table 4: IL19  (ok)

%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%%}

@@

\subsection*{1-2}
\label{page:1-2}
%
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

@@

After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it was shown here in the following paragraph.

\begin{MyColorPar}{red}
"%discussion: the third limitation
There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
"

%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」

%Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
%and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}.(see Figure \ref{fig:figure5}) %HNSCC
%dverse psychosocial experiences in early life, such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased risk of diabetes, heart disease, cancers, and psychiatric illnesses. 
%The possible molecular mechanisms could be also related with the mind-brain-body axis\cite{Berens2017}.
%Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}

% make Figure 5 holistic: Figure_5_holisticCare.pdf
%\begin{figure}[hp]
%...
%\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症

\end{MyColorPar} %red
\end{MyColorPar} % blue

%Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
%epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
%The usefulness of multi-omics data for the prediction of HNSCC outcome %is expected.
%such as the (censored) survival time.

@@

% strategy should changing; run GCP Rstudio? hard work to do
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.

@@

\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
"
The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data. It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:

@@

In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
"
\end{MyColorPar}

@@

\subsection*{2-6}
\subsubsection*{[Minor comments]}
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

@@

% (ok)
We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new Figure 1 with clear direction of the workflow.
A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
In Figure 2, the ticks and labels on the x-axis were corrected.\\[0.5cm]

%%
\begin{MyColorPar}{black} % minor comment
\subsubsection*{[Minor comments]}

More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
\end{MyColorPar}

Answer
We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.\\[0.3cm]

\begin{MyColorPar}{red}
% EdgeR
"
Some researchers\cite{Xu2021a} tried to find DEGs of gene expression data (without survival information) for HNSCC biomarker discovery.
RNA-Seq data were downloaded from The Cancer Genome Atlas (TCGA) database or other GSE datasets (e.x. GSE30784: 167 OSCC samples and 45 normal controls) from the Gene Expression Omnibus. 
They employed DAVID (https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function. 
The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was used to annotate the potential functions.
%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
The protein-protein interaction (PPI) network was conducted to identify differentially expressed genes (DEGs) closely associated with HNSCC.
The pathway enrichment analysis of DEGs was performed by DAVID, String, and Sytoscape software programs\cite{Huang2019}\cite{Shen2019}.
The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software. Moreover, genes with degree $>= 25$ were selected as hub genes. Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.

By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses. The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software. GOfunctional annotation and KEGG pathway analyses were performed using the Database for Annotation, Visualization, and Integrated Discovery. Hub genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA) and the Human Protein Atlas (HPA) website.

@@

% Cox Risk Regression Establishment and Validation with lncRNA data
HNSCC samples were randomly divided into a training set and a validation set. Univariate Cox regression was used to select prognosis-associated genes (\textit{p} value $< 0.05$). Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
establish a prognostic risk score model, and the penalty regularization parameter lambda ($\lambda$) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
%https://glmnet.stanford.edu/articles/glmnet.html
Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation
Finally, a validation set and Kaplan–Meier survival curves along with a logrank p test were applied to validate its accuracy. In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
Biomarkers Screening and Validation
The status and survival time of HNSCC patients were extracted. Subsequently, the mRNA was enrolled in the PPI and ceRNA networks, and lncRNA and miRNA identified in ceRNA were selected for screening biomarkers. We used univariate Cox regression to screen prognostic factors (p $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{p} value < 0.01) were selected as primitive biomarkers. 
Ultimately, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers. In addition, a combination of two or more biomarkers was performed to predict HNSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.

%\subsubsection{from TCGA to expression biomarkers} 
%%% how other researchers used TCGA to find expression biomarkers
Usually, researchers used TCGA to find expression biomarkers:\\
% reference https://www.biostars.org/p/153013/
Tutorial: Survival analysis of TCGA patients
#integrating gene expression (RNASeq) data Why would you want to do survival
#analysis based on gene expression data? Well, let's say you have a number of
#genes that you are interested in and they are differentially expressed between
#tumor and normal samples, it would be very powerful to show that alteration in
#gene expression correlates with worse survival or earlier tumor recurrence.
% https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
% from Mary Goldman and Jing Zhu, UCSC Cancer Browser
% https://genome-cancer.ucsc.edu/
"

@@

\begin{MyColorPar}{black} % minor comment
\subsubsection*{[Minor comments]}
%%%***[latex line 410]

In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.\\[0.3cm]
\end{MyColorPar}

@@

\begin{MyColorPar}{red}
%%%
There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.

First, although \acrshort{tcga} genomics data has been harmonized, 
%two things were found during our investigating and data cleaning:
the preprocessing of TCGA RNA-Seq is as follows:

\begin{outline}
\1 HNSCC samples without complete clinical information have been removed;

\1 Null expressed genes in more than 30\% or 50\% of the HNSCC samples have been excluded;

\1 After investigation of mRNA expression dataset, the number of protein-coding genes in the TCGA HNSCC should be updated as 20500 (instead of 20499);
%
we found that different expression value of gene SLC35E2.
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
% updated on 18-May-2021
\end{outline}

### 2021-06-03 main.tex
Updates from Overleaf

\acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
The tables were generated by latex code with the help from https://github.com/JDMCreator/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
We like to thank Dr. Wen-Chang Wang,
%https://orcid.org/0000-0003-3124-2136
College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
We like to thank Sylvain Hall\'e, Department of Computer Science and Mathematics, Univerit\'e du Qu\'ebec \`a Chicoutimi, Canada, for latex technique help with his TeXtidote.
%We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
% *** URL Accessed 20 May 2013.
The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/\newline
mtbwi/index.do. Accessed 20 May 2020.}

>>>>

\acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
The tables were generated by latex code with the help from https://www.tablesgenerator.com/latex_tables# and https://github.com/JDMCreator/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
We like to thank Dr. Wen-Chang Wang,
%https://orcid.org/0000-0003-3124-2136
College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
We like to thank Sylvain Hall\'e, Department of Computer Science and Mathematics, Univerit\'e du Qu\'ebec \`a Chicoutimi, Canada, for latex technique help with his TeXtidote.
%We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
% *** URL Accessed 20 May 2013.
The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/\newline
mtbwi/index.do. Accessed 20 May 2020.}
